\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{changepage}

\title{Info 98 Project 2 - Decal Syllabus}
\author{Intro to Dessert 137: Travel Asia with your Taste Bud}
\date{\small Spring 2019, Lecture T 10-11 AM, Lab R 10-12 PM}

\begin{document}
\maketitle
\hrulefill
\section{About the Course}
\subsection{Instructor(s) Information}
\underline{Student Instruction Team:} \\
$\cdot$ Amanda Ma (amma@berkeley.edu) \phantom{space}
$\cdot$ Esha Madhekar (esma@berkeley.edu) \\
$\cdot$ Zihan Wen (ziwe@berkeley.edu) \phantom{.....space}
$\cdot$ Yutong Wu (yuwu@berkeley.edu) \\ \\
\textbf{Office}: Stove Hall, Floor 2, Room 36B \phantom{.....space}
\textbf{Office Hours}: TR 9-10 AM, 3-5 PM

\subsection{Course Description:}
Welcome to \textit{Dessert 137: Travel Asia with your Taste Bud}! This is the first of many courses especially designed to introduce the beauty of Asian desert. You will not only learn about the histories of several Asian desserts, but also sharpen your practical cooking skills through hands on experience. 

\subsection{Expectations}
This class is a 2-unit, project-based, Pass/No-Pass course. We do not require previous cooking experience or knowledge in the history or making of Asian desserts. This course consists of 6 in-class projects, several reading assignments, and 6 1-page long reflections on projects and reading assignments. We evaluate your performance on the satisfactory completion of these projects, assignments, and reflections.
We encourage interested students of all majors to enroll in this course. There are no prerequisites and all student facilitators will provide you with whatever support you need.

\subsection{Learning Objectives}
Throughout this course we encourage you to develop your understanding by being able to participate in labs every two weeks, and engage with the material during lecture. Throughout the course we hope to solidify your understanding and introduce you to the art of making Asian Desserts from three Asian countries: Thailand, India and China. We hope you can engage with the material and develop a strong understanding through the hands-on labs, reflections, and reading assignments!

\hrulefill 

\section{Resources}
\subsection{Required Text}
There are no required texts for this course. \\ However, there will be several reading assignments given as specified. (see Readings and Assignments section)

\subsection{Recommended reading List}

\begin{itemize}
    \item Lucky Peach presents 101 easy Asian recipes / Peter Meehan 
    \begin{itemize}
        \item There is a section in this book that focused on Asian dessert
    \end{itemize}
    \item The language of food : a linguist reads the menu / Dan Jurafsky
    \begin{itemize}
        \item Although it does not specifically focus on Asian dessert, it is still a fun book to read that relates dessert and other food to linguistic. 
    \end{itemize}
\end{itemize}

\noindent We highly recommend completing reading assignments before coming to class for discussion. 

\hrulefill 
\section{Course Calendar}
\textit{\small *Calendar is subject to changes. Please check your email frequently for updates. Note that if a lecture occurs on a Thursday, the course is an hour long.}

\subsection*{Introductions}
\vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
 Lecture 1 & 1/22/2019  & Course Intro \& Logistics & Amanda Ma\\
\hline
 Lecture 2 &  1/24/2019 & The Kitchen: Anatomy, Pots, \& Utensils & Amanda Ma\\
\hline
 Lecture 3 &  1/29/2019 & Cooking Safety \& Common Hazards & Amanda Ma\\
\hline
 Lecture 4 & 1/31/2019 & Cooking Productivity \& Time Management & Amanda Ma\\
\hline
\end{tabular}

\subsection*{Theme 1: Indian}
\vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
 Lecture1 &  2/5/2019 & How to Make Jalebi & Esha Madhekar\\
\hline
 Lab 1 &  2/7/2019 & Make Jalebi yourself! & Esha Madhekar\\
\hline
Lecture 2 &  2/12/2019 & How to Make Kaju Katli & Esha Madhekar\\
\hline 
Lab 2 & 2/14/2019 & Make Kaju Katli yourself! & Esha Madhekar\\
\hline
\end{tabular}

\subsection*{Theme 2: Chinese }
\vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
Lecture 3 & 2/19/2019 & How to make a salted egg yolk ice cream mooncake & Zihan Wen\\
\hline
Lab 3 & 2/21/2019 & Make a mooncake yourself!& Zihan Wen\\
\hline
Lecture 4 & 2/26/2019 & How to make dragon beard candy & Zihan Wen\\
\hline 
Lab 4 & 2/28/2019 & Make dragon beard candy yourself!& Zihan Wen\\
\hline
\end{tabular}


 \subsection*{Theme 3: Thai }
 \vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
Lecture 5 & 3/5/2019 & How to make salted mango sorbet
 & Yutong Wu\\
\hline
Lab 5 & 3/7/2019 & Make salted mango sorbet yourself!& Yutong Wu\\
\hline
Lecture 6 & 3/12/2019 & How to make coconut pudding & Yutong Wu\\
\hline 
Lab 6 & 3/14/2019 & Make coconut pudding yourself!& Yutong Wu\\
\hline
\end{tabular}

\subsection*{History}
\vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
Lecture 5 & 3/19/2019 & History of Indian Dessert & Amanda Ma\\
\hline
Lab 5 & 3/21/2019 & Indian Desserts Discussion & Amanda Ma\\
\hline
Lecture 6 & 4/2/2019 & History of Chinese Dessert & Esha Madhekar\\
\hline 
Lab 6 & 4/4/2019 & Chinese Desserts Discussion & Esha Madhekar\\
\hline
Lecture 7 & 4/9/2019 & History of Thai Dessert & Zihan Wen\\
\hline 
Lab 7 & 4/11/2019 & Thai Desserts Discussion & Zihan Wen \\
\hline
\end{tabular}

 \subsection*{Quiz Period}
 \vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
Lecture 8 & 4/16/2019 & Quiz: The Kitchen: Anatomy, Pots \& Utensils & Amanda Ma\\
\hline
Lecture 9 & 4/18/2019 & Quiz: Cooking Safety \& Common Hazards & Amanda Ma\\
\hline
Lecture 10 & 4/23/2019 & Quiz: Cooking Productivity \& Time Management & Esha Madhekar\\
\hline 
Lecture 11 & 4/25/2019 & Quiz: Indian Desserts History & Esha Madhekar\\
\hline
Lecture 12 & 4/29/2019 & Quiz: Chinese Desserts History & Zihan Wen\\
\hline 
Lecture 13 & 5/2/2019 & Quiz: Thai Desserts History & Zihan Wen \\
\hline
***** & 5/7/2019 & FINAL EXAM & Yutong Wu \\
\hline
\end{tabular}

\vspace{1em}
\par\noindent\rule{\textwidth}{0.4pt}
  
\noindent\textbf{Readings and assignments} \\
\textit{\small Remember to complete reading assignments before lecture!} \\ \\
\vspace{0.5em} \begin{tabular}{|l|l|l|l|}
\hline 
Due 1/24 & https://en.wikipedia.org/wiki/Kitchen \\
\hline
Due 1/29 & https://publicsafety.tufts.edu/firesafety/cooking-safety/\\
\hline
Due 1/31 & https://www.lifehack.org/9.html \\
\hline
Due 2/5 & www.makejalebi.com \\
\hline
Due 2/12 & www.makekaju.com\\
\hline
Due 2/19 & www.makeseyicm.com\\
\hline 
Due 2/26 & www.makedbc.com\\
\hline 
Due 3/5 & www.makesms.com\\
\hline 
Due 3/12 & www.makecocopudding.com\\
\hline 
Due 3/19 & www.indiandesserts.com \\
\hline
Due 4/2 & www.chinesedesserts.com \\
\hline
Due 4/9 & www.thaidesserts.com \\
\hline
\end{tabular}\\
Optional:
\begin{itemize}
\item Watch a youtube video https://www.youtube.com/watch?v=fVmdWMLtEgY (Mooncake tutorial by Amanda tastes (7 min, optional)
\item Design your own mooncake flavor and list all the ingredients 
\item Watch a youtube video https://www.youtube.com/watch?v=Z2Zl64cSmpo("I Made The Impossible Cotton Candy From Ancient China 
\end{itemize}
  \par\noindent\rule{\textwidth}{0.4pt}
\textbf{Accommodations }
\begin{itemize}
\vspace{0.5em} 
\item\noindent The course will make reasonable accommodations for person with documented disabilities. Students should notify the Center for Disability Services office and their instructors of any special needs. Instructors should be notified as soon as possible.

 \end{itemize}
  \par\noindent\rule{\textwidth}{0.4pt}

\section{Grading Rubrics} 

To pass this class you will need a passing grade of 60\%. 

\begin{table}[h]
\begin{tabular}{lll}
 Attendance &  25\% \\
 Cooking/ Lab Work & 30\%  \\
 Reflections &  10\%  \\
 Participation & 10\% \\ 
 Quizzes & 10\% \\
 Final & 15\%
\end{tabular}
\end{table}   

\noindent Below, each of the categories is explained in detail:

\subsection{Attendance}
 The attendance grade is based on how many classes you attend. Every class you will be given a code that you have to input in a Google Form so we will know if you came to class! You have 1 unexcused absence. Afterwards, your attendance grade will decrease by 5\% per absence unless proof of medical emergencies, family emergencies, etc. is provided. 

\subsection{Cooking/ Lab Work} This grade will be mostly based on the amount of effort and attentiveness you show during lab. Maintaining a clean workspace and leaving with a clean space will also be 50\% of this grade. Even though we hope that everyone will be able to leave with a well-made dish we know that his may not always be possible so this will only count towards 20\% of the cooking grade.

\subsection{Reflections} Your reflections will be graded for accuracy and including information contained in readings as well as discussed during class. We generally expect reflections to be one page long, doubled spaced, 12-point font, and in Times New Roman. 

\subsection{Participation/Team Work} We will track participation during cooking labs, lecture, and discussions. Your conduct, eagerness to learn through answering/asking questions, and discussion contributions constitute most of your participation/teamwork grade.  

\subsection{Quizzes}
Quizzes are meant for solidifying your understanding of Asian dessert cultures. Your quiz scores reflect your participation and dedication towards this course. Note that quizzes are worth 10\% of your grade and there are 6 quizzes in total. There are no makeup quizzes except under unusual circumstances. If you miss a quiz, your score for that quiz will be 0. 

\subsection{Final}
This is a fun final! Half of the questions will focus on material covered over the semester, where you will be graded on correctness. The second half is free response, where you will be graded on whether you attempted the question. 

\end{document}
